\morus: Biases in the Stream

### 2018-05-10 morusAC_02_Preliminaries.tex
Proofreading

The encryption process of \MORUS consists of four parts: initialization, associated data processing, encryption, and finalization. 
During the initialization phase, the value of the state is initialized using a key and nonce.
Associated data block and plaintext blocks are then processed block by block.
Then the internal state undergoes the finalization phase, which outputs the authentication tag.

@@

The state is then updated with $S^{t+1} \leftarrow \StateUpdate{}(S^t, A^t)$ for $t=0,1,\ldots,\ell$ where $\ell = \lceil \frac{{\it adlen}}{128} \rceil -1$ and $\ell = \lceil \frac{{\it adlen}}{256} \rceil -1$ for \MORUS[640] and \MORUS[1280], respectively.

>>>>

The encryption process of \MORUS consists of four parts: initialization, associated data processing, encryption, and finalization. 
During the initialization phase, the value of the state is initialized using a key and nonce.
The associated data and the plaintext are then processed block by block.
Then the internal state undergoes the finalization phase, which outputs the authentication tag.

@@

The state is then updated with $S^{t+1} \leftarrow \StateUpdate{}(S^t, A^t)$ for $t=0,1,\ldots,u-1$ where $u = \lceil \frac{{\it adlen}}{128} \rceil$ and $u = \lceil \frac{{\it adlen}}{256} \rceil$ for \MORUS[640] and \MORUS[1280], respectively.
